Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-12 paper.tex
Add TSR to foil geometric considerations figure
Make estimate on viscous effects

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{figures/foil_kinematics_ct}
\caption{Geometric angle of attack, relative velocity and torque coefficient
calculated with a NACA 0020 foil.}
\label{fig:blade-kinematics}
\end{figure}

@@

We see that in general, levels of turbulent transport are slightly lower at
larger Reynolds numbers. The viscous diffusion and dissipation, though still
three orders of magnitude smaller than the other terms, do increase at low
Reynolds numbers, which is consistent with the physical meaning of the Reynolds
number in general.

\todo[inline]{At what $Re$ will the viscous terms get large enough to start
messing with the balance of the equation?}

>>>>

\includegraphics[width=0.9\textwidth]{figures/foil_kinematics_ct}

\caption{Geometric angle of attack, relative velocity and torque coefficient
    calculated with a NACA 0020 foil operating at $\lambda=1.9$.}

\label{fig:blade-kinematics}
\end{figure}

@@

We see that in general, levels of turbulent transport are slightly lower at
larger Reynolds numbers. The viscous diffusion and dissipation, though still
three orders of magnitude smaller than the other terms, do increase at low
Reynolds numbers, which is consistent with the physical meaning of the Reynolds
number in general. From these results one might expect that the viscous effects
will become significant to the wake dynamics around $Re_D \sim 10^4$.
